---
title: Increase Reproducibility of Research by Interactive Robustness Sections
subtitle: |
  |  A Step Towards Open Science in Empirical Accounting Resarch
author: | 
  | Joachim Gassen 
  | Humboldt-Universität zu Berlin
date:  |
  | `r loc <- Sys.getlocale(category = "LC_TIME"); Sys.setlocale("LC_TIME", "C"); fdate <- format(Sys.time(), '%B %d, %Y'); Sys.setlocale("LC_TIME", loc); fdate`
output: beamer_presentation
header-includes:
- \usepackage{booktabs}
- \usepackage{graphicx}
- \usepackage{media9}
- \usepackage{xcolor}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, table.align = "center", cache.lazy = FALSE, message = FALSE, error = FALSE, warning = FALSE, clean = FALSE)
library(knitr)
opts_knit$set(root.dir = "..", fig.pos = 'h')
library(kableExtra)
library(captioner)
library(animation)

install_pkg_if_missing_and_attach <- function(pkg_string) {
  lib_str <- strsplit(pkg_string, "/")[[1]][length(strsplit(pkg_string, "/")[[1]])]
  if (!require(lib_str, character.only = TRUE)) {
    if (!grepl("/", pkg_string)) install.packages(pkg_string,repos = "http://cran.us.r-project.org")
    else devtools::install_github(pkg_string)
    library(lib_str, character.only = TRUE)
  }
} 

pkgs <- c("devtools", "Quandl", "gtools", "ggpubr", "lfe",
          "tidyverse", "joachim-gassen/ExPanDaR",
          "lubridate", "broom", "tweenr", "moments",
          "Hmisc", "RCurl", "nteetor/gganimate", "scales")

invisible(lapply(pkgs, install_pkg_if_missing_and_attach))

# Set the below to TRUE when you want repull consumer price data (needs to be done at least once)

refresh <- TRUE


# Set the below to TRUE if you want repull Compustat data from WRDS 
# This also needs to be done at least once and can also be done by running
# code/fetch_wrds_data.R directly.
#
# NOTE: code/fetch_wrds_data.R needs editing prior to sourcing!
#
# Refer to the Appendix in the paper for additional guidance

fetch_wrds_data <- FALSE
```

``` {r utils, include=FALSE}
source("code/utils.R")
source("code/samples.R")
source("code/tables.R")
source("code/figures.R")
source("code/videos.R")
```

``` {r sample, include=FALSE, cache=TRUE}
if (fetch_wrds_data) source("code/fetch_wrds_data.R", local = new.env())

list2env(prepare_us_samples(), environment())
list2env(prepare_int_samples(), environment())
us_ys <- prepare_us_yearly_sample(test_sample)
int_ys <- prepare_int_yearly_sample(all20_ctry_sample)
```

# Motivation

## We publish many significant studies \dots

\begin{center}
\includegraphics[height=0.7\textheight]{../media/fanelli_2010_PLoS_one.jpg} \\
Fanelli (PLoS one, 2010)
\end{center}


## \dots but face a replication crisis

\begin{center}
\includegraphics[width=0.8\textwidth]{../media/osc_science_2015.jpg} \\
Open Science Collaboration (Science, 2015)
\end{center}


## Data and code repositories are on the rise \dots

\begin{center}
\includegraphics[width=0.8\textwidth]{../media/gertler_galiani_romero_nature_fig1_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}


## \dots but often fail to guarantee reproducible results

\begin{center}
\includegraphics[height=0.8\textheight]{../media/gertler_galiani_romero_nature_fig2_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}

# Case Study

## Bushman, Lerman and Zhang (JAR, 2016)

\begin{equation}
\label{level_reg}
TACC = \beta_0 + \beta_1 CFO + \epsilon
\end{equation}

```{r fig_blz_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_blz_results()
```

## Explanations explored by BLZ

\setlength{\itemsep}{\fill}

1. Increase in cash flows/economic earnings volatility \textcolor{red}{\text{\sffamily X}}
2. Increase of non-timing-related accruals \textcolor{green}{\checkmark}
3. Poorer matching of revenues and expenses  \textcolor{red}{\text{\sffamily X}}
4. Increasing importance of intangible intensive firms  \textcolor{red}{\text{\sffamily X}}
5. Accruals increasingly reflect the timely loss recognition rule  \textcolor{red}{\text{\sffamily X}}

# Reproduction

## Key finding of BLZ reproduces well

\begin{equation}
TACC = \beta_0 + \beta_1 CFO + \epsilon \tag{\ref{level_reg} revisited}
\end{equation}

```{r fig_level_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_rep_blz_results(us_ys, "level", "cfo")
```

# Exploration

## $CFO$ $TACC$ association over time

\includemedia[
  width=\textwidth, height=0.67\textwidth, keepaspectratio,
   activate=pageopen,
 addresource=test_sample_cfo_tacc_scatter_3_by_2.mp4,
 flashvars={source=test_sample_cfo_tacc_scatter_3_by_2.mp4
 &loop=true
    }
 ]{}{VPlayer.swf}

## Expand BLZ: [https://jgassen.shinyapps.io/expacc/](https://jgassen.shinyapps.io/expacc/)

\begin{center}
\includegraphics[width=\textwidth]{../media/blz_table_4.jpg} \\
BLZ (JAR, 2016)
\end{center}

# Conclusion

## Conclusion

* Many studies in empirical archival accounting are designed as if they would provide confirmatory evidence while they actually provide exploratory evidence.
* This implies that they fail to realize all of their exploratory potential
* Visuals make data shine 
* Open source and data allow us to progress faster
* Interactive robustness checking helps to provide some benefits of replications at very low cost

## Links

* Code: [https://github.com/joachim-gassen/ExpAcc](https://github.com/joachim-gassen/ExpAcc)
* R Package: [https://joachim-gassen.github.io/ExPanDaR/](https://joachim-gassen.github.io/ExPanDaR/)
* Expand: [https://jgassen.shinyapps.io/expacc/](https://jgassen.shinyapps.io/expacc/)
* Blog: [http://arc.eaa-online.org/blog/interactive-robustness-sections-step-towards-open-science](http://arc.eaa-online.org/blog/interactive-robustness-sections-step-towards-open-science)