---
title: Reporoducible Exploratory Data Analysis
subtitle: |
  |  A Step Towards Open Science in Empirical Accounting Resarch
author: | 
  | Joachim Gassen 
  | Humboldt-Universität zu Berlin
date:  |
  | `r loc <- Sys.getlocale(category = "LC_TIME"); Sys.setlocale("LC_TIME", "C"); fdate <- format(Sys.time(), '%B %d, %Y'); Sys.setlocale("LC_TIME", loc); fdate`
output: beamer_presentation
header-includes:
- \usepackage{booktabs}
- \usepackage{graphicx}
- \usepackage{media9}
- \usepackage{xcolor}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, table.align = "center", cache.lazy = FALSE, message = FALSE, error = FALSE, warning = FALSE, clean = FALSE)
library(knitr)
opts_knit$set(root.dir = "..", fig.pos = 'h')
library(kableExtra)
library(captioner)
library(animation)

install_pkg_if_missing_and_attach <- function(pkg_string) {
  lib_str <- strsplit(pkg_string, "/")[[1]][length(strsplit(pkg_string, "/")[[1]])]
  if (!require(lib_str, character.only = TRUE)) {
    if (!grepl("/", pkg_string)) install.packages(pkg_string,repos = "http://cran.us.r-project.org")
    else devtools::install_github(pkg_string)
    library(lib_str, character.only = TRUE)
  }
} 

pkgs <- c("devtools", "Quandl", "gtools", "ggpubr", "lfe",
          "tidyverse", "joachim-gassen/ExPanDaR",
          "lubridate", "broom", "tweenr", "moments",
          "Hmisc", "RCurl", "nteetor/gganimate", "scales")

invisible(lapply(pkgs, install_pkg_if_missing_and_attach))

# Set the below to TRUE when you want repull consumer price data (needs to be done at least once)

refresh <- TRUE


# Set the below to TRUE if you want repull Compustat data from WRDS 
# This also needs to be done at least once and can also be done by running
# code/fetch_wrds_data.R directly.
#
# NOTE: code/fetch_wrds_data.R needs editing prior to sourcing!
#
# Refer to the Appendix in the paper for additional guidance

fetch_wrds_data <- FALSE
```

``` {r utils, include=FALSE}
source("code/utils.R")
source("code/samples.R")
source("code/tables.R")
source("code/figures.R")
source("code/videos.R")
```

``` {r sample, include=FALSE, cache=TRUE}
if (fetch_wrds_data) source("code/fetch_wrds_data.R", local = new.env())

list2env(prepare_us_samples(), environment())
list2env(prepare_int_samples(), environment())
us_ys <- prepare_us_yearly_sample(test_sample)
int_ys <- prepare_int_yearly_sample(all20_ctry_sample)
```

``` {r scatter_video, include=FALSE, cache=TRUE, eval = FALSE}
create_scatter_video(test_sample, "Test sample", x="cfo", y="tacc", 
                     size="avg_at_cpi2014", size_legend="Average AT (2014 prices)",
                     color="ff12ind", color_legend="FF 12 industry", fsize = 18,
                     filename = "presentation/test_sample_cfo_tacc_scatter_3_by_2.mp4",
                     ani.width=1500, ani.height=1000, loess = TRUE)
```


# Motivation

## We publish many significant studies \dots

\begin{center}
\includegraphics[height=0.7\textheight]{../media/fanelli_2010_PLoS_one.jpg} \\
Fanelli (PLoS one, 2010)
\end{center}


## \dots but face a replication crisis

\begin{center}
\includegraphics[width=\textwidth]{../media/osc_science_2015.jpg} \\
Open Science Collaboration (Science, 2015)
\end{center}


## Data and code repositories are on the rise \dots

\begin{center}
\includegraphics[width=0.8\textwidth]{../media/gertler_galiani_romero_nature_fig1_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}


## \dots but often fail to guarantee reproducible results

\begin{center}
\includegraphics[height=0.8\textheight]{../media/gertler_galiani_romero_nature_fig2_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}

## Exploratory data analysis

\begin{center}
\includegraphics[width=\textwidth]{../media/ijgi-06-00368-g001.png} \\
Ma et al. (IJGI, 2017)
\end{center}


## Bushman, Lerman and Zhang (JAR, 2016)

\begin{equation}
\label{level_reg}
TACC = \beta_0 + \beta_1 CFO + \epsilon
\end{equation}

```{r fig_blz_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_blz_results()
```


## Explanations explored by BLZ

\setlength{\itemsep}{\fill}

1. Increase in cash flows/economic earnings volatility \textcolor{red}{\text{\sffamily X}}
2. Increase of non-timing-related accruals \textcolor{green}{\checkmark}
3. Poorer matching of revenues and expenses  \textcolor{red}{\text{\sffamily X}}
5. Increasing importance of intangible intensive firms  \textcolor{red}{\text{\sffamily X}}
5. Accruals increasingly reflect the timely loss recognition rule  \textcolor{red}{\text{\sffamily X}}

## Evidence offered by BLZ

\begin{center}
\includegraphics[width=\textwidth]{../media/blz_table_4.jpg} \\
BLZ (JAR, 2016)
\end{center}


# Replication

## Key finding of BLZ replicates well

\begin{equation}
TACC = \beta_0 + \beta_1 CFO + \epsilon \tag{\ref{level_reg} revisited}
\end{equation}

```{r fig_level_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_rep_blz_results(us_ys, "level", "cfo")
```

# Robustness

## Result is stable across size deciles

``` {r fig_level_by_at, cache = TRUE, echo = FALSE}
prepare_fig_level_by_at(test_sample, "cfo_est")
```


## Result is stable across industries

``` {r fig_level_by_ind, cache = TRUE, echo = FALSE}
prepare_fig_level_by_ind(test_sample, "cfo_est")
```


## Result is not stable across $CFO$ deciles

``` {r fig_level_by_cfo, cache = TRUE, echo = FALSE}
prepare_fig_level_by_cfo(test_sample, "cfo_est")
```

# Exploration

## $CFO$ $TACC$ association over time

\includemedia[
  width=\textwidth, height=0.67\textwidth, keepaspectratio,
   activate=pageopen,
 addresource=test_sample_cfo_tacc_scatter_3_by_2.mp4,
 flashvars={source=test_sample_cfo_tacc_scatter_3_by_2.mp4
 &loop=true
    }
 ]{}{VPlayer.swf}

 
## $\beta_1$ and $CFO\_SD$ by $year$
``` {r fig_ys_sbs, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_ys_sbs(us_ys)
```


## Effect of $CFO$ distribution on time trend

``` {r tab_dist_tests_cfo, cache = TRUE, echo = FALSE, results = "asis"}

dist_test <- prepare_tab_impact_cfo_dist_us(us_ys)
dist_test[[1]]$table[12] <- "\\\\[-1.8ex] & cfo\\_est & cfo\\_est & cfo\\_est & cfo\\_est & cfo\\_est & cfo\\_est & cfo\\_est & resid\\_cfo \\\\ "
latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               "\\begin{tabular}{lcccccccc}",
               dist_test[[1]]$table[8:49],
               "\\end{tabular}}",
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))
```

Expand: [https://jgassen.shinyapps.io/expacc/](https://jgassen.shinyapps.io/expacc/)

# Extension

## International sample

```{r tab_world_sample, cache = TRUE, echo = FALSE, results = "asis"}
time_effects <- estimate_int_time_effect(int_ys)
kable(all20_ctry, format = "latex", booktabs = T, linesep = "",
      format.args = list(decimal.mark = ".", big.mark = ",", 
                         scientific=FALSE)) -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))
latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               lat_tab[2:31],
               "\\midrule",
               paste0("Total & & ", 
                      format(nrow(int_ys), big.mark = ","), 
                      " & ", 
                      format(nrow(all20_ctry_sample), big.mark = ","), 
                      "\\\\"),
               "\\bottomrule",
               "\\end{tabular}}", 
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))               
```


## $time$ effect and impact of $CFO$ distribution internationally

``` {r fig_time_effect_cfo_world_sbs, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_fig_time_effect_sbs(time_effects, "cfo")
```


## Regression results

``` {r tab_tests_world, echo=FALSE, cache = TRUE, results="asis"}
tab_tests_world <- prepare_tab_impact_cfo_dist_int(int_ys)
tab_tests_world$table[12] <- "\\\\[-1.8ex] & cfo\\_est & cfo\\_est & resid\\_cfo & adjr2 & adjr2 & resid\\_adjr2 \\\\ "
latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               "\\begin{tabular}{lcccccc}",
               tab_tests_world$table[8:46],
               "\\end{tabular}}",
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))
```


## Yearly fixed effects

``` {r fig_yearly_fixed_effects, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_fig_yearly_fixed_effects(int_ys, "resid_cfo")
```


# Conclusion

## Conclusion

* Many studys in empirical archival accounting are designed as if they would provide confirmatory evidence while they actually provide exploratory evidence.
* This implies that they fail to realize all of their exploratory potential
* Visuals make data shine 
* Open source and data allow us to progress faster
* Interactive robustness checking helps to provide some benefits of replications at very low cost

## Links

* Code: [https://github.com/joachim-gassen/ExpAcc](https://github.com/joachim-gassen/ExpAcc)
* R Package: [https://joachim-gassen.github.io/ExPanDaR/](https://joachim-gassen.github.io/ExPanDaR/)
* Expand: [https://jgassen.shinyapps.io/expacc/](https://jgassen.shinyapps.io/expacc/)
* Blog: [http://arc.eaa-online.org/blog/interactive-robustness-sections-step-towards-open-science](http://arc.eaa-online.org/blog/interactive-robustness-sections-step-towards-open-science)