---
title: Exploring the Accrual Landscape
author: | 
  | Martin Bierey and Joachim Gassen 
  | Humboldt-Universität zu Berlin
date:  |
  | `r loc <- Sys.getlocale(category = "LC_TIME"); Sys.setlocale("LC_TIME", "C"); fdate <- format(Sys.time(), '%B %d, %Y'); Sys.setlocale("LC_TIME", loc); fdate`
  | Interim Version
  
output: 
  beamer_presentation

header-includes:
- \usepackage{booktabs}
- \usepackage{graphicx}
- \usepackage{media9}
- \usepackage{xcolor}
- \usepackage{array}
- \setbeamertemplate{itemize subitem}{-}
- \titlegraphic{\includegraphics[width=2cm]{../media/husiegel_bw}}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, table.align = "center", cache.lazy = FALSE, message = FALSE, error = FALSE, warning = FALSE, clean = FALSE)
library(knitr)
opts_knit$set(root.dir = "..", fig.pos = 'h')
library(kableExtra)
library(captioner)
library(animation)

install_pkg_if_missing_and_attach <- function(pkg_string) {
  lib_str <- strsplit(pkg_string, "/")[[1]][length(strsplit(pkg_string, "/")[[1]])]
  if (!require(lib_str, character.only = TRUE)) {
    if (!grepl("/", pkg_string)) install.packages(pkg_string)
    else devtools::install_github(pkg_string)
    library(lib_str, character.only = TRUE)
  }
} 

pkgs <- c("devtools", "Quandl", "gtools", "ggpubr", "lfe",
          "tidyverse", "joachim-gassen/ExPanDaR",
          "lubridate", "broom", "tweenr", "moments",
          "Hmisc", "RCurl", "nteetor/gganimate", "scales",
          "latex2exp", "stringr")

invisible(lapply(pkgs, install_pkg_if_missing_and_attach))

# This code relies on the WRDS and some additional data 
# being present in the data/ directory. 
# 
# To make sure that this is the case, run 'produce_findings.R' 
# in the project's root directory prior to knitting this file.
#
# Refer to the Appendix in the paper for additional guidance

needed_data_files <- c("../data/cpiauscl.RDS",
                       "../data/iso3_country_names.RDS",
                       "../data/cstat_us_sample.RDS",
                       "../data/cstat_int_sample.RDS")
if (!all(file.exists(needed_data_files))) 
  stop("Data not downloaded. Please run 'produce_findings.R prior to knitting this file")

refresh <- FALSE
```

``` {r utils, include=FALSE}
source("code/utils.R")
source("code/samples.R")
source("code/tables.R")
source("code/figures.R")
source("code/videos.R")
```

``` {r sample, include=FALSE, cache=TRUE}
list2env(prepare_us_samples(), environment())
list2env(prepare_int_samples(), environment())
us_ys <- prepare_us_yearly_sample(test_sample)
int_ys <- prepare_int_yearly_sample(all20_ctry_sample)
```

``` {r scatter_video, include=FALSE, cache=TRUE}
create_scatter_video(test_sample, "Test sample", x="cfo", y="tacc", 
                     size="avg_at_cpi2014", size_legend="Average AT (2014 prices)",
                     color="ff12ind", color_legend="FF 12 industry", fsize = 18,
                     filename = "presentations/test_sample_cfo_tacc_scatter_3_by_2.mp4",
                     ani.width=1500, ani.height=1000, loess = TRUE)
```


# Motivation


## We face a replication crisis

\begin{center}
\includegraphics[width=\textwidth]{../media/osc_science_2015.jpg} \\
Open Science Collaboration (Science, 2015)
\end{center}


## Data and code repositories are on the rise \dots

\begin{center}
\includegraphics[width=0.8\textwidth]{../media/gertler_galiani_romero_nature_fig1_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}


## \dots but yet fail to guarantee reproducable results

\begin{center}
\includegraphics[height=0.8\textheight]{../media/gertler_galiani_romero_nature_fig2_2018.jpg} \\
Gertler, Galiani and Romero (Nature, 2018)
\end{center}


## Bushman, Lerman and Zhang (JAR, 2016)

\begin{equation}
\label{level_reg}
TACC_{i,t} = \beta_{0,t} + \beta_{1,t} CFO_{i,t} + \epsilon_{i,t}
\end{equation}

```{r fig_blz_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_blz_results()
```


## Explanations explored by BLZ

\setlength{\itemsep}{\fill}

1. Increase in cash flows/economic earnings volatility \textcolor{red}{\text{\sffamily X}}
2. Increase of non-timing-related accruals \textcolor{green}{\checkmark}
3. Poorer matching of revenues and expenses  \textcolor{red}{\text{\sffamily X}}
5. Increasing importance of intangible intensive firms  \textcolor{red}{\text{\sffamily X}}
5. Accruals increasingly reflect the timely loss recognition rule  \textcolor{red}{\text{\sffamily X}}


## [Key analysis of BLZ](https://jgassen.shinyapps.io/expacc/)

\begin{center}
\includegraphics[width=\textwidth]{../media/blz_table_4.jpg} \\
BLZ (JAR, 2016)
\end{center}


# Reproduction

## Variable definitions

```{r vardef, cache = TRUE, results="asis", echo = FALSE}
vd <- readRDS("raw_data/blz_var_definitions.RDS")
Variable <- paste0("$", gsub("_", "", toupper(vd[c(7:8, 11:12, 6, 5, 14), 1])), "_{i,t}$")
definition <- c(
  "$0.5AT_{t-1} + 0.5AT_t$",
  "$IB_t/AVGAT_t$",
  "If $(year > 1987)$ $(IBC_t - OANCF_t) / AVGAT_t$ else $(ACT_t - ACT_{t-1} - (CHE_{t} - CHE_{t-1}) - ((LCT_t - LAG_{t-1}) - (DLC_t - DLC_{t-1})) - DP_t) / AVGAT_t$",
  "If $(year > 1987)$ $OANCF_t / AVGAT_t$ else $E_t - TACC_t$",
  "$PRCCF_t * CSHO_t$",
  "$CEQ_t / MV_t$",
  "$XSGA_t /(SALE_t - IB_t)$"
  )
  
Description <- c(
  "Average total assets in M US-\\$",
  "Earnings deflated by average total assets",
  "Total accruals, derived from earnings and cash flow from operations as reported in the cash flow statement after 1987 and from the balance sheet before, deflated by average total assets",
  "Cash flow from operations, as reported in the cash flow statement after 1987 and derived from the balance sheet before, deflated by average total assets",
  "Market value of common stock in M US-\\$",
  "Book-to-market ratio based on common stock",
  "SG\\&A Intenisty: Share of total cost that can be attributed to selling, general and administrative expenses"
)

vt <- data.frame(Variable, definition, Description, stringsAsFactors = FALSE)
names(vt)[2] <- 'Compustat definition'

kable(vt, format = "latex",
      row.names = FALSE, booktabs = TRUE, escape = FALSE, linesep = "") -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))
lat_tab[5] <- "\\toprule"
new_lat_tab <- lat_tab[1:5]
for (i in 6:12) {
  new_lat_tab[2*i - 6] <- lat_tab[i]
  if (i != 12) new_lat_tab[2*i - 5] <- "\\midrule"
}
new_lat_tab <- c(new_lat_tab, lat_tab[13:length(lat_tab)])

latex_tab <- c("\\resizebox{\\textwidth}{!}{",
               "\\begin{tabular}{l>{\\raggedright}p{6cm}p{8cm}}",
               new_lat_tab[3:length(new_lat_tab)],
               "}")
cat(paste(latex_tab, collapse = "\n"))  
```


## Original BLZ sample

\includegraphics[width=1\textwidth]{../media/blz_table_1_panel_a.jpg}


## Our first try

```{r descriptives_rs, cache = TRUE, echo = FALSE, results="asis"}
t <- prepare_descriptive_table(rep_sample[, c("e", "tacc", "lagcfo", 
                                             "cfo", "leadcfo", "mv", 
                                             "bm", "sgaint")])
desc_rnames <- c("$E_{i,t}$", "$TACC_{i,t}$", "$CFO_{i,t-1}$", "$CFO_{i,t}$", "$CFO_{i,t+1}$", 
                    "$MV_{i,t}$", "$BM_{i,t}$", "$SGAINT_{i,t}$")
rownames(t$df) <- desc_rnames 
names(t$df)[c(5,7)] <- c("25 \\%", "75 \\%")
kable(t$df, digits = c(0, 3, 3, 3, 3, 3, 3, 3), format = "latex",
      format.args = list(decimal.mark = ".", big.mark = ",", 
                         scientific=FALSE),
      booktabs = TRUE, escape = FALSE, linesep = "") -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))

latex_tab <- c("\\resizebox{\\textwidth}{!}{",
               lat_tab[2:length(lat_tab)],
               "}")

cat(paste(latex_tab, collapse = "\n"))  

```


## After excluding obs with $AVGAT <$ M US-\$ 7.5

```{r descriptives_ts, cache = TRUE, echo = FALSE, out.width = "\\textwidth", results="asis"}

t <- prepare_descriptive_table(test_sample[, c("e", "tacc", "lagcfo", 
                                               "cfo", "leadcfo", "mv", 
                                               "bm", "sgaint")])
rownames(t$df) <- desc_rnames 
names(t$df)[c(5,7)] <- c("25 \\%", "75 \\%")

kable(t$df, digits = c(0, 3, 3, 3, 3, 3, 3, 3), format = "latex",
      format.args = list(decimal.mark = ".", big.mark = ",", 
                         scientific=FALSE),
      booktabs = TRUE, linesep = "", escape = FALSE) -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))

latex_tab <- c("\\resizebox{\\linewidth}{!}{",
               lat_tab[2:length(lat_tab)],
              "}")
cat(paste(latex_tab, collapse = "\n"))  

```


## Key finding of BLZ replicates well

\begin{equation}
TACC_{t,i} = \beta_{0,t} + \beta_{1,t} CFO_{t,i} + \epsilon_{t,i} \tag{\ref{level_reg} revisited}
\end{equation}

```{r fig_level_results, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_rep_blz_results(us_ys, "level", "cfo")
```

# Robustness

## Base model

\begin{equation}
  \label{time_reg}
  \beta_{1,t} = b_0 +b_1 TIME_t +\epsilon_t
\end{equation}


## Result is stable across size deciles

``` {r fig_level_by_at, cache = TRUE, echo = FALSE}
prepare_fig_level_by_at(test_sample, "cfo_est")
```


## Result is stable across industries

``` {r fig_level_by_ind, cache = TRUE, echo = FALSE}
prepare_fig_level_by_ind(test_sample, "cfo_est")
```


## Result is not stable across $CFO$ deciles

``` {r fig_level_by_cfo, cache = TRUE, echo = FALSE}
prepare_fig_level_by_cfo(test_sample, "cfo_est")
```


## $\beta_1$ and Adj. $R^2$ time trends by $CFO$ deciles

``` {r fig_level_by_cfo_comp, cache = TRUE, echo = FALSE}
prepare_fig_level_comp(test_sample, "cfo")
```


# Exploration

## $CFO$ $TACC$ association over time

\includemedia[
  width=\textwidth, height=0.67\textwidth, keepaspectratio,
   activate=pageopen,
 addresource=test_sample_cfo_tacc_scatter_3_by_2.mp4,
 flashvars={source=test_sample_cfo_tacc_scatter_3_by_2.mp4
 &loop=true
    }
 ]{}{VPlayer.swf}

 
## $\beta_1$ and $CFO\_SD$ by $year$

``` {r fig_ys_sbs, cache = TRUE, echo = FALSE, out.height="6cm", fig.align="center"}
prepare_fig_ys_sbs(us_ys)
```


## Effect of $CFO$ distribution on time trend

``` {r tab_dist_tests_cfo, cache = TRUE, echo = FALSE, results = "asis"}
dist_test <- prepare_tab_impact_cfo_dist_us(us_ys)
dist_test[[1]]$table[12] <- "\\\\[-1.8ex] & $\\beta_1$ & $\\beta_1$ & $\\beta_1$ & $\\beta_1$ & $\\beta_1$ & $\\beta_1$ & $RESID_{CFO}$ \\\\ "

latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               "\\begin{tabular}{lcccccccc}",
               dist_test[[1]]$table[8:14],
               toupper(sub(pattern = "(\\b[a-zA-Z\\\\_]+\\b)", "$\\1$", dist_test[[1]]$table[15:31])),
               dist_test[[1]]$table[32:(length(dist_test[[1]]$table) - 3)],
               "\\end{tabular}}",
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))
```


## [The table missing from BLZ $(n = 51)$](https://jgassen.shinyapps.io/expacc)

``` {r corr_yearly_us_sample, cache = TRUE, echo = FALSE, results="asis"}
tab <- prepare_correlation_table(us_ys[,c(3:8, 13, 17, 36, 37, 42)], 
                                 format = "latex", booktabs = TRUE, linesep = "")
tab$kable_ret <- gsub("%", "\\%", tab$kable_ret)
tab$kable_ret <- gsub("_", "\\\\_", tab$kable_ret)
lat_tab <- unlist(strsplit(tab$kable_ret, "\n"))
lat_tab[7:17] <- sub("(\\b[a-zA-Z2\\\\_]{2,}\\b)", "\\U$\\1$", lat_tab[7:17], perl = TRUE)
lat_tab[13] <- sub("\\$.*\\$", "$\\\\beta_1$", lat_tab[13])
lat_tab[14] <- sub("\\$.*\\$", "$Adj. R^2$", lat_tab[14])
lat_tab[15] <- sub("\\$.*\\$", "$RESID_{CFO}$", lat_tab[15])
lat_tab[16] <- sub("\\$.*\\$", "$RESID_{Adj. R^2}$", lat_tab[16])

latex_tab <- c("\\begin{center}",
               "\\resizebox*{\\textwidth}{!}{",
               "\\begin{tabular}{lccccccccccc}",
               lat_tab[3:19],
               "\\end{tabular}}",
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))
```


# International Replication and Extension

## International sample

```{r tab_world_sample, cache = TRUE, echo = FALSE, results = "asis"}
time_effects <- estimate_int_time_effect(int_ys)
df <- all20_ctry
names(df) <- c("ISO code", "Country", "# years", "# observations")
kable(df, format = "latex", booktabs = T, linesep = "",
      format.args = list(decimal.mark = ".", big.mark = ",", 
                         scientific=FALSE)) -> kab_latex

lat_tab <- unlist(strsplit(kab_latex, "\n"))

latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               lat_tab[2:31],
               "\\midrule",
               paste0("Total & & ", 
                      format(nrow(int_ys), big.mark = ","), 
                      " & ", 
                      format(nrow(all20_ctry_sample), big.mark = ","), 
                      "\\\\"),
               "\\bottomrule",
               "\\end{tabular}}", 
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))               
```


## $TIME$ effect and impact of $CFO$ distribution internationally

``` {r fig_time_effect_cfo_world_sbs, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_fig_time_effect_sbs(time_effects, "cfo")
```


## [Regression results](https://jgassen.shinyapps.io/expacc)

``` {r tab_tests_world, echo=FALSE, cache = TRUE, results="asis"}
tab_tests_world <- prepare_tab_impact_cfo_dist_int(int_ys)
tab_tests_world$table[12] <- "\\\\[-1.8ex] & $\\beta_1$ & $\\beta_1$ & $RESID_{CFO}$ & $Adj. R^2$ & $Adj. R^2$ & $RESID_{Adj. R^2}$ \\\\ "
latex_tab <- c("\\begin{center}",
               "\\resizebox*{!}{0.8\\textheight}{",
               "\\begin{tabular}{lcccccc}",
               tab_tests_world$table[8:14],
               sub(pattern = "(\\b[a-zA-Z\\\\_]+\\b)", "\\U$\\1$", tab_tests_world$table[15:31], perl = TRUE),
               tab_tests_world$table[32:(length(tab_tests_world$table) - 3)],
               "\\end{tabular}}",
               "\\end{center}")
cat(paste(latex_tab, collapse = "\n"))
```


## Yearly fixed effects

``` {r fig_yearly_fixed_effects, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_fig_yearly_fixed_effects(int_ys, "resid_cfo")
```


## US: The effect is centered in the 80s/90s \dots

``` {r fig_rolling_bs, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_rolling_bs_figure(test_sample, 10, "level", "adjr2")
```


## \dots and is driven by new firms and certain industries

``` {r fig_corr_change_by_ind, out.height = "8cm", cache = TRUE, echo=FALSE}
prepare_fig_corr_change_by_ind(test_sample)
```


# Conclusion

## Wrapping up and next steps

* ~80% of the temporal effect documented by BLZ can be explained by changes in cash flow distribution over time.
* International data documents a remaining time trend that
    - is most pronounced in the 80s/90s and
    - is driven by young firms and tech industries
* This seems inconsistent with an accounting standards based explanation
* Some potential reasons for the drastic change in the cash flow distribution across time:
    - Changes in database coverage
    - More early stage life cycle firms in recent years
    - Firms with longer operating cycles in recent years
    - Less tangible investment in recent years (replacing CFI by CFO)  
* Open science: Everybody is invited to explore these issues further by building on our analyses! 
